---
name: Kaleb
surname: Ducharme
position: "Student"
address: "Department of Molecular, Cellular, and Biomedical Sciences; University of New Hampshire" 
phone: (603) 948 5346

email: "Kaleb.ducharme@unh.edu"
github: "Kale-23"

headcolor: 414141 # use black color
date: "`r format(Sys.time(), '%B %Y')`"
csl: apa-cv.csl 
output: 
  vitae::awesomecv:
    pandoc_args: [--lua-filter="lua/strong.lua"]
  latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
#options(tinytex.verbose = TRUE)

```

<!-- # Research Interests -->

<!-- Bioinformatics, Comparative Transcriptomics, Evolutionary Biology -->

# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where, ~ GPA,

  "Master of Science, Genetics",
  "Expected 2025",
  "University of New Hampshire",
  "Durham, New Hampshire",
  "Current GPA: 4.00",

  "Bachelor of Science, Neuroscience and Behavior",
  "May 2023",
  "University of New Hampshire",
  "Durham, New Hampshire",
  "Summa cum Laude"

) %>%
  detailed_entries(
    what = Degree,
    when = Year,
    with = Institution,
    where = Where,
    why = GPA
  )
```

# Awards

```{r}
tribble(
  ~Year, ~Name, ~Institution, ~Supp, ~Amount,

  "2019-2023",
  "Presidential Scholarship",
  "University of New Hampshire",
  NA,
  "$5,000/year",

  "4/2023",
  "Award of Excellence",
  "University of New Hampshire",
  "URC poster presentation",
  NA

) %>%
  detailed_entries(
    where = Year,
    with = Name,
    what = Institution,
    why = Supp,
    when = Amount
  )
```

# Research Experience

```{r}
tribble(
  ~ Advisor, ~ Year, ~ Lab, ~ Where, ~ Points,

  "Masters Student - Advisor: Dr. David Plachetzki",
  "9/2023 - Present",
  "Plachetzki Lab",
  "University of New Hampshire",
  list("Utilizing and developing bioinformatic tools and pathways to analyze the complete transcriptomes of diverse hagfish species contributing to a comprehensive understanding of the protein products within slime glands",
       "Investigating the evolutionary history of hagfish slime by tracking variations in the genetic makeup of selected genes across species, providing insight into novel adaptations"),
  
  "Extension Intern",
  "5/2023 - 8/2023",
  "Lakes Lay Monitoring Program",
  "University of New Hampshire",
  list("Developed methodology and analysis for qPCR study using python and R into cyanobacteria populations on Lake Winnipesaukee",
       "Enhanced community engagement in cyanobacteria bloom research through working with local committee",
       "Assisted in collection, processing, and presentation of quality metrics for lakes in the NH region"),
  
  "Research Assistant - Advisor: Dr. Omer Daglar Tanrikulu",
  "9/2022 - 5/2023",
  "Visual Perception Lab",
  "University of New Hampshire",
  list("Developed virtual reality experimental methodology to study ensemble perception using the python coding lanuage and Vizard development package",
       "Processed participants through experiment",
       "Created R script to automatically clean and output data visualizations used in final presentation"),
  
  "Independent Study - Advisor: Dr. Caitlyn Mills",
  "1/2022 - 5/2022",
  "Affect, Cognition, & Computation Lab ",
  "University of New Hampshire",
  list("Processed participants through virtual reality experimentation procedures",
       "Developed python and R analysis pipelines to clean up and analyze raw eye-tracking data"),

) %>%
  detailed_entries(
    what = Advisor,
    when = Year,
    with = Lab,
    where = Where,
    why = Points
  )
```

# Presentations

```{r}
bibliography_entries("presentations.bib")
```

# Teaching Experience

``` {r}
tribble(
  ~Position, ~Year, ~Institution, ~Location, ~Details,
  
  "Graduate Teaching Assistant - BCMB659: General Biochemistry Lab",
  "8/2023 - 12/2023",
  "University of New Hampshire",
  "Durham, New Hampshire",
  "Taught two sections of students, graded lab reports, and helped lab instructor to overhaul class content"
  
) %>%
  detailed_entries(
    with = Position,
    when = Year,
    what = Institution,
    where = Location,
    why = Details
  )
```

# Relevant Skills

**Coding Languages:** Bash, Python, Java, R

**Software:** Slurm managed computer cluster use, ChimeraX, qiime2 commandline bioinformatics platform, Benchling virtual plasmid digestion, Microsoft suite

**Laboratory:** Spectrophotometry, Recombinant protein expression in *E. coli*, Purification of target protein using AKTA start chromatography system (Affinity, gel filtration), SDS-Page, qPCR techniques





