---
name: Kaleb
surname: Ducharme
position: "Student"
address: "21 Copper Ln, Rochester, NH 03868"
phone: (603) 948 5346
#www: 
email: "Kaleb.ducharme@unh.edu"
#github:
#twitter: 
headcolor: 414141 # use black color
date: "`r format(Sys.time(), '%B %Y')`"
csl: apa-cv.csl 
output: 
  vitae::awesomecv:
    pandoc_args: [--lua-filter="lua/strong.lua"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
rmarkdown::pandoc_version()
```

# Research Interests

I have been in a biological sciences based major, but through lab experiences I have gained knowledge in some data science techniques. I plan to advance my knowledge further through research in bioinformatics, geonomics, and similar areas.

# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where, ~ Course,

  "Bachelor of Science, Neuroscience and Behavior -Current GPA: 3.97",
  "Expected May 2023",
  "University of New Hampshire",
  "Durham, New Hampshire",
  "Relevant Coursework: Biostatistics 1, 
  General Chemistry, 
  Organic Chemistry, 
  Biochemistry, 
  Principles of Genetics, 
  Human Genetics, 
  Intro to Computer Science (Python and Java), 
  Data Science for Life Sciences (in progress),
  Endocrinology (in progress)",

) %>%
  detailed_entries(
    what = Degree,
    when = Year,
    with = Institution,
    where = Where,
    why = Course,
  )
```

# Awards
```{r}
tribble(
  ~Year, ~Name, ~Institution, ~Supp, ~Amount,

  "2019-2022",
  "Presidential Scholarship",
  "University of New Hampshire",
  NA,
  "$5,000/year"

) %>%
  detailed_entries(
    where = Year,
    with = Name,
    what = Institution,
    why = Supp,
    when = Amount
  )
```

# Research Experience

## Affect, Cognition, & Computation Lab
*Research Assistant for Credit* Spring Semester 2022  
Advisor: Dr. Caitlyn Mills  
Ran participants through virtual reality experiments to assess various paradigms of mind wandering. Cleaned the raw data output of the eye-tracking hardware and survey software using Python and R. Analyzed the cleaned data using R and presented initial results.

## Visiual Perception Lab 
*Volunteer Research Assistant* Fall Semester 2022 - Present  
Advisor: Dr. Omer Daglar Tanrikulu  
Currently in the early stages of designing ensemble perception experiments in a virtual reality setting. Advancing knowledge in Python and learning to use the Vizard software (Python based VR development tool) to create the VR experiment.


# Presentations

```{r}
bibliography_entries("presentations.bib")
```

# Technical Skills

## Complutational
Intermediate Knowledge in Python and Java, R, Microsoft Suite

## Wet Lab
Spectrophotometry, Recombinant protein expression in *E. coli*, Benchling for virtual plasmid digestions, Purification of target protein using AKTA start chromatography system (Affinity, gel filtration), SDS-Page, Analysis of active sites of proteins in Chimera


